\documentclass{res} %[11pt]
\usepackage{palatino}
\usepackage{fancyhdr}
\usepackage{xcolor}
\usepackage[pdftex,colorlinks=true]{hyperref} %\href{url}{text}

\setlength{\textheight}{9.5in}
\newsectionwidth{0pt}
\pagenumbering{arabic}
\pagestyle{plain}
\fancyhf{}

\newcommand{\Cpp}{C\ensuremath{+\!\,\!\,\!\,+\,\,}}

\begin{document}

\name{Dr. Alexis Jawtuschenko, PhD.}
\begin{resume}
\bigskip
 
\input{history-en}

\end{resume}
\end{document}

Esto lo escribi para Solvd:
1- At MercadoLibre (2020 - 2022) I used a MacBook Pro, because the company had that already decided,
to write a complete optimization tool including a Linear Programming model for some logistics operations
research problems that we had at the depots/warehouses. 
My development framework was Python, IBM CPLEX, Pandas, NumPy, Git, GitHub, Mac Os.
As the stakeholders and final users of the tool were Windows users, for the releases I came with the
idea of getting the company to purchase a single license of Parallels Desktop, and then I was able to fluently
release a simple standalone '.exe' console application, with the help of PyInstaller, to use on 
Windows machines.

2- For the consultation work for my first thesis (2009) that was much simpler because I had a native
Windows operating system installed on my machine (I think it was Windows XP), so I directly compiled 
my project into a console application in an exe file.

Cover letter
I am in love with the development of software for applied mathematics, and particularly in modern C++.
I like the task of enhancing and optimizing the performance of pieces of code, whether they were 
written by me or not, and I can confidently 
state that I am pretty good at it, and that includes the patience and
the perseverance of my code-debugging proficiency. This task is also one that I like, because it has
a strong flavor of the very fundamental activity that a mathematician is supposed to do: to look for
a working solution of an open question, and doing the math starting from the darkness of the ignorance 
about the issue.

TODO: 26/02/2025 Poner links a lo  que escribi para la UBA. Poisson, guias de
      ejercicios (optim, mefa, etc). El texto de combin. aucti. Los teoremas de An I


------------------------------------------------------------------------------
\textbf{Current Occupation}\\[6pt]
  Freelance programmer
------------------------------------------------------------------------------


------------------------------------------------------------------------------
Trabajos Publicados en Actas de Conferencias\\

A. Jawtuschenko, A. Lombardi: \emph{Estimaciones de interpolaci\'on en pir\'amides con aplicaciones a problemas mixtos con singularidades de arista y v\'ertice}, Res\'umenes de Comunicaciones UMA 2016, p. 1, LXV Reuni\'on de Comunicaciones Cient\'ificas.
\\[4pt]

A. Jawtuschenko, A. Lombardi: \emph{Anisotropic Estimates for $H(\textbf{curl})$ and $H(\textrm{div})$ -- Conforming Elements On Prisms and Applications}, Trabajos presentados al V MACI 2015. MACI Vol. 5 pp. 141 -- 142.\\[4pt]

A. L. Lombardi, A. Jawtuschenko. {\it Estimaciones de interpolaci\'on
para elementos finitos vectoriales sobre ma\-llas poli\'edricas anisotr\'opicas}. Cuaderno de Res\'umenes de Comu\-ni\-caci\-on\-es UMA 2015, LXIV Reuni\'on de Comunicaciones Cient\'ificas.\\[4pt]

A. Jawtuschenko, A. Lombardi: \emph{Estimaci\'on Anisotr\'opica para Elementos de N\'ed\'elec Prism\'aticos}, Cuaderno de Res\'umenes de Comunicaciones UMA 2014, p. 35, LXIII Reuni\'on de Comunicaciones 
Cient\'ificas. 
--------------------------------------------------------------------


--------------------------------------------------------------------
\textbf{Antecedentes De Divulgaci\'on de la Matem\'atica}\\[6pt]
Semana de la Matem\'atica,  Departamento de Matem\'atica, FCEyN, UBA,
ediciones entre 2005 y 2019.\\[4pt]
El Departamento de Matem\'atica en la Feria del Libro 2019.\\[4pt]
Un Festival de Ciencia, Centro Cultural Konex, 2018.\\[4pt]
Exactas en La Noche de los Museos, 2017.\\[4pt] 
Exactas en Tecn\'opolis, 2012.\\[4pt]
IV Festival de Matem\'atica de la Reuni\'on anual de la Uni\'on Ma\-te\-m\'a\-ti\-ca
Argentina en la Academia Nacional de Ciencias, Ciudad de C\'ordoba,
edici\'on 2012.
--------------------------------------------------------------------
